---
title: "Strip Test Plots"

---

# Load libraries
library(tidyverse)
library (tidyr)
library(ggplot2)
library(reshape2)
library(dplyr)
library(facetscales)
library(forcats)
library(devtools)
library(ggpubr)
library(cowplot)

### Make strip test plot

#Read data
data.table <- read.table("temperaturecoral.csv",h=T,sep=",")

```{r}
head(data.table)
```

# Make blank data frame (replace with own values)
blanks <- data.frame(Sample = ("Blank"),
                     Leukocytes = (231.423),
                     Glucose = (229.2186),
                     Ketone = (197.2447)
                  )

# Subtract blank values from strip test values
data.table <- data.table%>%
                       mutate(Leukocytes_Norm = blanks$Leukocytes - Leukocytes)

data.table <- data.table%>%
                       mutate(Ketone_Norm = blanks$Ketone - Ketone)

data.table <- data.table%>%
                       mutate(Glucose_Norm = blanks$Glucose - Glucose)
```{r}
head(data.table)
```
                       
# Format data for proper plotting order of 2019 data
sapply(data.table, mode)
mode(data.table$Genotype) <-'character'

# Make separate table for each species and format data for proper plotting order of 2021 wild sample data
data.table$Reef <- as.character(data.table$Reef)
data.table$Colony <- factor(data.table$Colony, order=TRUE, levels=1:16)
Pacuta.data <- data.table[grep("Pacuta", data.table$Species), ]
Mcap.data <- data.table[grep("Mcapitata", data.table$Species), ]
Pcomp.data <- data.table[grep("Pcompressa", data.table$Species), ]

# Plot strip test results for one test at a time
a <- ggplot(data.table, aes(x=Condition, y=Ketone_Norm)) + 
  geom_boxplot() +
  geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.8,aes(fill=Condition)) +
  facet_grid(. ~ Species,scales = "free") +
  theme(legend.position = "none") +
  xlab("Treatment") +
  ylab("Relative enzymatic activity") +
  ggtitle("Ketone test thermal stress (2021)") 

# Plot all strip test results for one species/experiment & one test to view variability
b <- ggplot(data.table, aes(x=Species, y=Ketone_Norm)) + 
  geom_boxplot() +
  geom_dotplot(binaxis='y', stackdir='center', dotsize = 0.8,aes(fill=Condition)) +
  facet_grid(. ~ Species,scales = "free") +
  theme(legend.position = "right") +
  xlab("All samples") +
  ylab("Relative enzymatic activity") +
  ggtitle("Variation in ketone test") 

# Combine 2 plots
figure <- ggarrange(a, b,
                    labels = c("A", "B"),
                    ncol = 1, nrow = 2,
                    widths = c(1, 1),
                    common.legend = TRUE, legend = "bottom")

figure

# End