---
title: "Strip Test PCA Plots"
---

# Loading library
library(ggfortify)
library(ggbiplot)
library(scales)
library(devtools)
library(ggpubr)

# Load files
strip_values <- read.table("temperaturecoral.csv", header=T, sep=',')
```{r}
head(strip_values)
```
```{r}
sapply(strip_values, mode)
sum(is.na(strip_values))
```

# Make separate table for each species
Pacuta.data <- strip_values[grep("Pacuta", strip_values$Species), ]
Mcap.data <- strip_values[grep("Mcapitata", strip_values$Species), ]
Pcomp.data <- strip_values[grep("Pcompressa", strip_values$Species), ]

# Create PCA object - 1 species
Pacuta.pca <- prcomp(Pacuta.data[,c(5:6)],
                   center = TRUE,
                   scale. = TRUE)

# Create PCA object - 1 species
Mcap.pca <- prcomp(Mcap.data[,c(5:6)],
                     center = TRUE,
                     scale. = TRUE)

# Create PCA object - 1 species
Pcomp.pca <- prcomp(Pcomp.data[,c(5:6)],
                     center = TRUE,
                     scale. = TRUE)

# Summary of the prcomp object
```{r}
summary(Mcap.pca)
```

# Structure of the PCA object
```{r}
str(Mcap.pca)
```

# Plot for each species
a <- ggbiplot(Pacuta.pca,
                          data = Pacuta.data,
                          obs.scale = 1, 
                          var.scale=1,
                          ellipse=T,
                          circle=F,
                          varname.size=3,
                          var.axes=T,
                          groups=Pacuta.data$Condition) +
                          labs(title="P. acuta PCA")

b <- ggbiplot(Mcap.pca,
              data = Mcap.data,
              obs.scale = 1, 
              var.scale=1,
              ellipse=T,
              circle=F,
              varname.size=3,
              var.axes=T,
              groups=Mcap.data$Condition) +
              theme(legend.position = "None") +
              labs(title="M. capitata PCA")

c <- ggbiplot(Pcomp.pca,
              data = Pcomp.data,
              obs.scale = 1, 
              var.scale=1,
              ellipse=T,
              circle=F,
              varname.size=3,
              var.axes=T,
              groups=Pcomp.data$Condition) +
              labs(title="P. compressa PCA")
              
# End              